### 2016-09-30 GBF-correctness-private-M.tex
bf and gbf

@@

\oracle{$\HashOracle(\qry_y)$}\\
for $j \in \{1,2,\ldots,k\}$\\
\nudge $v_j \getsr [m]$\\
\nudge if $T[j,y] \neq \undefined$\\
\nudge \nudge $v_j \gets T[j,y]$\\
\nudge $T[j,y] \gets v_j$\\
Ret $\left(v_1,\ldots,v_k\right)$
}
}
\caption{Games $\game{0}$-$\game{3}$ for the
proof of Theorem~\ref{thm:gbf-correctness}.}
\label{fig:gbf-correctness-games1}
\end{figure}
\begin{figure}[tp]
\fpage{.95}{
\hpagessl{.4}{.5}
{
\underline{$\game{4}(A)$\fbox{$\game{5}(A)$}}\\
$c\gets 0$, $\bad \gets \false$\\
$\err \gets 0$;  $\calC \gets \emptyset$\\
$S \getsr A$\\
$\mathcal{I}\getsr [\{1,2,\ldots,q_T + q_H\}]^r$\\
$(\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
$\bot \getsr A^{\TestOracle}(\pubaux)$\\
if $\bad = \true$ then \fbox{Return 0}\\
if $\err  < r$ then Return 0\\
Return 1\\

\oracle{$\TestOracle(\qry_x)$}\\
if $x \in \mathcal{C}$ then Return $\bot$\\
$\calC \gets \calC \cup x$\\
if $\Ans[x] = \undefined$\\
\nudge $(h_1, \ldots, h_{k}) \gets \HashOracle(\qry_x)$\\
Return $\Ans[x]$\\
}
{
\oracle{$\HashOracle(\qry_y)$}\\
$c \gets c + 1$\\
for $j \in \{1,2,\ldots,k\}$\\
\nudge $v_j \getsr [m]$\\
%
$M \gets\privaux$\\
$y' \gets M[v_1] \xor M[v_2] \xor \ldots \xor M[v_k]$\\
if $y' \neq y$ then \\
\nudge $\Ans[y] \gets (0, (v_1, \ldots, v_{k}) )$\\
\nudge if $c \in \calI$ then $\bad \gets \true$\\
\nudge Return $\left(v_1,\ldots,v_k\right)$\\
if $c \notin \calI$ then $\bad \gets \true$\\
$\err \gets \err +1$\\
$\Ans[y] \gets (1, (v_1, \ldots, v_{k}))$\\
Return $\left(v_1,\ldots,v_k\right)$
}
}
%
\fpage{.95}{
\hpagessl{.4}{.5}
{
\underline{$\game{6}(A)$}\\
$c\gets 0$, $\bad \gets \false$\\
$\err \gets 0$;  $\calC \gets \emptyset$\\
$S \getsr A$\\
$\mathcal{I}\getsr [\{1,2,\ldots,q_T + q_H\}]^r$\\
$(\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
$\bot \getsr A^{\TestOracle}(\pubaux)$\\
if $\bad = \true$ then \fbox{Return 0}\\
if $\err  < r$ then Return 0\\
Return 1\\

\oracle{$\TestOracle(\qry_x)$}\\
if $x \in \mathcal{C}$ then Return $\bot$\\
$\calC \gets \calC \cup x$\\
if $\Ans[x] = \undefined$\\
\nudge $(h_1, \ldots, h_{k}) \gets \HashOracle(\qry_x)$\\
Return $\Ans[x]$\\
}
{
\oracle{$\HashOracle(\qry_y)$}\\
$c \gets c + 1$\\
for $j \in \{1,2,\ldots,k\}$\\
\nudge $v_j \getsr [m]$\\
%
$M \gets\privaux$\\
$y' \gets M[v_1] \xor M[v_2] \xor \ldots \xor M[v_k]$\\
if $y' \neq y$ then \\
\nudge $\Ans[y] \gets (0, (v_1, \ldots, v_{k}) )$\\
\nudge if $c \in \calI$ then $\bad \gets \true$\\
\nudge Return $\left(v_1,\ldots,v_k\right)$\\
if $c \notin \calI$ then $\bad \gets \true$\\
$\err \gets \err +1$\\
$\Ans[y] \gets (1, (v_1, \ldots, v_{k}))$\\
Return $\left(v_1,\ldots,v_k\right)$
}
}
\caption{Games $\game{4}$-$\game{5}$ for the
proof of Theorem~\ref{thm:gbf-correctness}.}
\label{fig:gbf-correctness-games2}
\end{figure}
\hfill\qed
\end{proof}

>>>>

We note that since game~$\game{5}(A)$ returns iff~$A$ manages to find~$r$ errors the game managed to guess exactly which $\HashOracle$ queries would cause the errors, there is a zero-query adversary~$A_0$ that manages to find~$r$ errors. Namely, adversary~$A_0$

@@

\oracle{$\HashOracle(\qry_y)$}\\
for $j \in \{1,2,\ldots,k\}$\\
\nudge $v_j \getsr [m]$\\
\nudge if $T[j,y] \neq \undefined$\\
\nudge \nudge $v_j \gets T[j,y]$\\
\nudge $T[j,y] \gets v_j$\\
Ret $\left(v_1,\ldots,v_k\right)$
}
}
\caption{Games $\game{0}$-$\game{3}$ for the
proof of Theorem~\ref{thm:gbf-correctness}.}
\label{fig:gbf-correctness-games1}
\end{figure}
\begin{figure}[tp]
\fpage{.85}{
\hpagessl{.45}{.5}
{
\underline{$\game{4}(A)$\fbox{$\game{5}(A)$}}\\
$c\gets 0$, $\bad \gets \false$\\
$\err \gets 0$;  $\calC \gets \emptyset$\\
$S \getsr A$\\
$\mathcal{I}\getsr [\{1,2,\ldots,q_T + q_H\}]^r$\\
$(\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
$\bot \getsr A^{\TestOracle,\HashOracle}(\pubaux)$\\
if $\bad = \true$ then \fbox{Return 0}\\
if $\err  < r$ then Return 0\\
Return 1\\

\oracle{$\TestOracle(\qry_x)$}\\
if $x \in \mathcal{C}$ then Return $\bot$\\
$\calC \gets \calC \cup x$\\
if $\Ans[x] = \undefined$\\
\nudge $(h_1, \ldots, h_{k}) \gets \HashOracle(\qry_x)$\\
Return $\Ans[x]$\\
}
{
\oracle{$\HashOracle(\qry_y)$}\\
$c \gets c + 1$\\
for $j \in \{1,2,\ldots,k\}$\\
\nudge $v_j \getsr [m]$\\
%
$M \gets\privaux$\\
$y' \gets M[v_1] \xor M[v_2] \xor \ldots \xor M[v_k]$\\
if $y' \neq y$ then \\
\nudge $\Ans[y] \gets (0, (v_1, \ldots, v_{k}) )$\\
\nudge if $c \in \calI$ then $\bad \gets \true$\\
\nudge Return $\left(v_1,\ldots,v_k\right)$\\
if $c \notin \calI$ then $\bad \gets \true$\\
$\err \gets \err +1$\\
$\Ans[y] \gets (1, (v_1, \ldots, v_{k}))$\\
Return $\left(v_1,\ldots,v_k\right)$
}
}
%
\fpage{.85}{
\hpagessl{.45}{.5}
{
\adversaryv{$A_0(\pubaux)$}\\
$c\gets 0$, $\calY \gets \emptyset$\\
$\calC \gets \emptyset$\\
$\mathcal{I}\getsr [\{1,2,\ldots,q_T + q_H\}]^r$\\
$\bot \getsr A^{\TestOracle,\HashOracle}(\pubaux)$\\
Return~$\calY$

\oracle{$\TestOracle(\qry_x)$}\\
if $x \in \mathcal{C}$ then Return $\bot$\\
$\calC \gets \calC \cup x$\\
if $\Ans[x] = \undefined$\\
\nudge $(h_1, \ldots, h_{k}) \gets \HashOracle(\qry_x)$\\
Return $\Ans[x]$\\
}
{
\oracle{$\HashOracle(\qry_y)$}\\
$c \gets c + 1$\\
for $j \in \{1,2,\ldots,k\}$\\
\nudge $v_j \getsr [m]$\\
%
if $c \not\in \calI$ then \\
\nudge $\Ans[y] \gets (0, (v_1, \ldots, v_{k}) )$\\
\nudge Return $\left(v_1,\ldots,v_k\right)$\\
$\calY \gets \calY \cup \{y\}$\\
$\Ans[y] \gets (1, (v_1, \ldots, v_{k}))$\\
Return $\left(v_1,\ldots,v_k\right)$
}
}
\caption{Games $\game{4}$-$\game{5}$ and zero-query adversary~$A_0$ for the
proof of Theorem~\ref{thm:gbf-correctness}.}
\label{fig:gbf-correctness-games2}
\end{figure}
\hfill\qed
\end{proof}
